Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
Copy-edit abstract

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every project version of the repository by using a
popular static analysis tool. Then by taking advantage of
the repository's features (multiple versions for every project, dependencies) we studied
the evolution of security bugs through time. In addition, we examined
their persistence and their relationship with a) the
size of the corresponding version and b) other bug categories. Our findings
indicate that there is no simple relationship between the number of
security bugs and project evolution. In particular, we
cannot say that across projects defect counts increase or decrease
significantly over time. Furthermore, security bugs are not eliminated in a
way that is particularly different from the other bugs. Also, the relation of
such bugs with size appears to be different from the relation of the bugs
coming from other categories. Finally, even if bugs seem to have similar behaviour,
severe security bugs seem to be dissociated with other categories.
\end{abstract}

>>>>

\begin{abstract}
%\boldmath
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every project version of the repository by using a
popular static analysis tool. Then by taking advantage of
the repository's project history and dependency data we studied
the evolution of security bugs through time. In addition, we examined
their persistence and their relationship with
a) the size of the corresponding version, and
b) other bug categories.
Our findings indicate that there is no simple rule governing the number of
security bugs as a project evolves.
In particular, we cannot say that across projects security-related
defect counts increase or decrease significantly over time.
Furthermore, security bugs are not eliminated in a
way that is particularly different from the other bugs.
In addition, the relation of security bugs with a project's size
appears to be different from the relation of the bugs
coming from other categories.
Finally, even if bugs seem to have similar behaviour,
severe security bugs seem to be unassociated with other bug categories.
\end{abstract}
